---
title: "w3w sandbox"
author: "Jesse L. and Heather G. Patsolic"
output: 
  html_document:
    keep_md: true
---

<!--
### ### INITIAL COMMENTS HERE ###
###
### Jesse Leigh Patsolic 
### 2018 <Jesse.L.Patsolic@alumni.wfu.edu>
### S.D.G 
#
-->

```{r render, eval=FALSE, echo=FALSE}
require(rmarkdown)
rmarkdown::render("Blank.Rmd")
system('open Blank.html')
```

<style type="text/css">
.table {
    width: 40%;
}
tr:hover {background-color:#f5f5f5;}
</style>

## What 3 Words

[what3words](https://map.what3words.com/kicked.tennis.clever?utm_campaign=B2C_4561_W3_Pt_Core%252BApp_BothOs_Org_WO_en_Main%252BSite%252BCarousel&utm_medium=dynamic_link&utm_source=w3w)

The idea of **what 3 words** has many interesting applications and one
of the first ideas that comes to mind is package delivery. Amazon could,
in theory, request the 3-word coordinate for where someone would like
their package delivered and send a drone directly to that location.
However, we know that sending information is not always correct. 
The website advertises that similar triples of words are far away from
each other geographically, and I began to wonder if this were true and
where packages could end up if there were minor deviations in the names.
In particular, which locations have triples of words that are similar to
each other.

## Idea

So, I set out to sample (not so randomly) roughly 100 triples of words,
obtaining 100 data points which would form the vertices of a graph.
I then placed an edge between any pair of vertices, $i$ and $j$, that
had a word in common (set-wise).
[](that was given by the Hamming Distance between the two vertices.)
In the API, you can search for partial words, but at least one letter
for each of the three words must be specified, and only three locations
are given for each querry.
[](In order to pull sets of words that would have low Hamming Distance, 
I chose words, such as "farmer, sharp, bliss, radar, coffee" etc)
In order to ensure the graph had edges, I thought of some words and
searched for (word,letter,letter) for many words. 

<!--
**Definition:** In information theory, the **Hamming Distance** between
two strings of equal length is the number of positions at which the
corresponding symbols are different. See [Hamming Distance
WikiPage](https://en.wikipedia.org/wiki/Hamming_distance) for more
information.
-->

## Data Preparation 

Since I am more fluent in R, I first attempted to retrieve data from
w3w's API using their "threewords" package in R. However, this ended up
being severely limited. Instead I wound up using Python to download
3-word locations along with with long/lat coordinates using the w3w API. 

### In order to use the API with R: 

```{r cc1}
require(threewords)
f <- file('w3w.conf', 'r')
jkey <- readLines(f)
close(f)
```


```{r}
tmp <- from_words(key, 'coffee')
from_words(key = jkey, words = c('index', 'home', ''))

from_position(key = jkey, positions = c(6.385336,-36.293769), lang = 'fr')


tmp <- httr::GET(url = paste0('https://api.what3words.com/v2/autosuggest?addr=plan.clips.a&focus=51.4243877,-0.3474524&clip=bbox(54,2,50,-4)&lang=en&key=', jkey))


tmp <- httr::GET(url = paste0("https://api.what3words.com/v2/standardblend?addr=plan.clips.above&lang=en&focus=51.4243877,-0.3474524&format=json&key=", jkey))

```

### In order to use the API with Python: 

Insert stuff here!!!

## Using Data From w3w API from Python

The data have been imported and set up using Python

```{r json}
f <- file('store_dat.json', 'r')
h <- rjson::fromJSON(file = f)
close(f)
load(dat.RData)
```




<!--
#   Time:
##  Working status:
### Comments:
####Soli Deo Gloria
--> 

