---
title: "w3w graph"
author: "Jesse Leigh Patsolic"
output: 
  slidy_presentation:
    font_adjustment: -1
  html_document:
    keep_md: true
---

<!--
### ### INITIAL COMMENTS HERE ###
###
### Jesse Leigh Patsolic 
### 2018 <Jesse.L.Patsolic@alumni.wfu.edu>
### S.D.G 
#
-->

```{r render, eval=FALSE, echo=FALSE}
require(rmarkdown)
require(threewords)
require(data.table)
require(igraph)
library("ggmap")
library(maptools)
library(maps)
rmarkdown::render("graph.Rmd", output_format = 'slidy_presentation')
system('open graph.html')
```

<style type="text/css">
.table {
    width: 40%;
}
tr:hover {background-color:#f5f5f5;}
</style>


# What is what3words?

A unique three word address for every 3m X 3m square on earth.

## Users

- The Red Cross
- Mercedes-Benz (for in-car voice nav.)

## example

[ClarkHall_w3w](https://map.what3words.com/kicked.tennis.clever?utm_campaign=B2C_4561_W3_Pt_Core%252BApp_BothOs_Org_WO_en_Main%252BSite%252BCarousel&utm_medium=dynamic_link&utm_source=w3w)

# Data Preparation 

I used the w3w API to download and store addresses with their location
to a JSON file. I then load it into R.

```{r cc1}
f <- file('../Python/store_data.json', 'r')
store <- rjson::fromJSON(file = f)
close(f)
```

# Get each three word address 

```{r}
words <- 
  Reduce(c,
  lapply(store, function(tmp) {
      Reduce(c, 
        lapply(tmp[[2]], function(x) {
               t1 <- 
                 x$words
               }
        )
      )
  })
)
ind <- duplicated(words)
uwords <- words[!ind]
```


# Extract three words and lon/lat into data.frame

```{r}
dat <- 
Reduce(rbind, 
  lapply(store, function(tmp) {
    Reduce(rbind, 
      lapply(tmp[[2]], function(x) {
             
             t1 <- 
               rbind(strsplit(x$words, split = '[.]')[[1]])
      
             t2 <- 
               rbind(c(lat = x$geometry$lat, lng = x$geometry$lng))
      
             data.table(t1, t2)
             }
      )
    )
  })
)
udat <- dat[!ind,]
```

# instantiate adjacency matrix

```{r}
n <- nrow(udat)
A <- matrix(0, n,n)
sord <- order(udat$lng, udat$lat)
```

# flip edges on 

```{r}
uset <- unique(c(udat[[1]], udat[[2]], udat[[3]]))
ulist <- lapply(uset, function(u) grepl(u, uwords))

for (ul in ulist) {
  for (i in 1:n) {
    for (j in 1:n) {
      if (i != j & ul[i] & ul[j]) { 
        A[i,j] <- 1
      }
    }
  }
}
#plot(raster(A[sord, sord]), col = c('white', 'green'))
#image(A[sord, sord])
image(A, col = c('white', 'darkgreen'))
```

# create graph

```{r}
g1 <- igraph::graph_from_adjacency_matrix(A, mode = 'undirected')
lo <- layout.norm(as.matrix(udat[, c(5,4)]))
```


# map edges for easy plotting in ggplot

```{r}
edgelist <- get.edgelist(g1)
edges <- data.frame(udat[edgelist[,1], c(5,4)], udat[edgelist[,2], c(5,4)])
colnames(edges) <- c("X1","Y1","X2","Y2")
```

# build ggplot

```{r, fig.width = 12, fig.height = 8, fig.retina = 2}
#Using GGPLOT, plot the Base World Map
mp <- NULL
mapWorld <- borders("world", colour="gray35", fill="gray50", 
                    ylim = range(udat$lat) + c(-1,1))
mp <- ggplot() + mapWorld
mp <- mp + geom_segment(aes(x = X1, y = Y1, xend = X2, yend = Y2), 
             data = edges, size = 0.5, colour = 'gray75', alpha = 0.025) +
           geom_point(aes(x=udat$lng, y=udat$lat) ,color="red", cex=0.05)
```

# The Map

```{r, echo = FALSE, fig.width = 14, fig.heigth = 10}
print(mp)
```


# table of words

```{r}
tab <- table(c(udat[[1]], udat[[2]], udat[[3]]))
tab
```


<!--
#   Time:
##  Working status:
### Comments:
####Soli Deo Gloria
--> 

